---
title: "corona"
#output: html_document

output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source_code: embed

---

```{r setup, include=FALSE}
library(plyr)
library(flexdashboard)
library(tidyverse)
library(scales)
library(lubridate)
library(gridExtra)
library(openintro)
library(rvest)
library(jsonlite)
```

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```


```{r, include=FALSE}
###############################################################
###############################################################
# Definition and Scripts 

# Turn off scientific notation
options(scipen=999)

# Define colors
cb.blue <- "#0072B2"
cb.orange <- "#E69F00"
cb.purple <- "#CC79A7"
cb.red <- "#D55E00"
cb.black <- "#000000"

cb.six <- c("#000000",  
            cb.blue, 
            cb.orange, cb.purple,
            "#56B4E9", "#009E73" )
cb.seven <- c("#009E73", cb.blue, "#000000",
              "#999999", 
              cb.orange, cb.purple, cb.red) #"red")

cb.8 <- c("#009E73", cb.blue, "#000000",
              "#999999", 
              cb.orange, cb.purple, "red", "maroon")


clr.ww.conf = cb.orange
clr.us.conf = cb.blue
clr.ww.dead = 'darkred'
clr.us.dead = cb.purple

###############################################################
###############################################################
# hard code in 1 million so I don't fat finger it later
mill <- 1000000

###############################################################
###############################################################

# Population Statistics
michpop <- 10000000
ohpop <- 11700000
txpop <- 28700000
wipop <- 5800000
capop <- 39600000
nypop <- 19500000
wapop <- 7500000
flpop <- 21500000

## worldwide pop
italypop <- 61000000
frpop <- 65000000
gerpop <- 84000000
chpop <- 1439000000
uspop <- 327000000
skpop <- 51000000
spainpop <- 47000000

###############################################################
###############################################################

# American War Deaths
#  From Wikipedia

civil.war <- 750000
WW2 <- 405399
WW1 <- 116516
nam <- 58209
korean.war <- 54246
iraq.war <- 4576
afg <- 2216

###############################################################
###############################################################

# Per 1 million population graph
#     a = df
#     type = conf, act, death, recovered
#     region = one of the following:
#             State for US plot; or Country.Reg for worldwide plot
#     typex = conft, act, death, recovered

graph.my.data.per1mm <- function(a, type, region, typex) {
  ggplot(a, aes(x = date, y = type, na.rm = TRUE,
               color = region,
               group = region
    )) +
    geom_point(size = 3) + 
    geom_line(size = 2) +
    scale_colour_manual(values = cb.seven) +
    scale_x_date(date_labels="%b %d",date_breaks  ="1 week") +
    scale_y_continuous(labels = comma) +
    #xlab("Date") +
    ylab("per 1 Million Population") +
    theme(panel.grid.minor = element_blank()) +
    guides(color = guide_legend(title = NULL)) +
    theme_bw() +
    theme(legend.text = element_text(size = 14)) +
    theme(axis.text.x = element_text(size = 13, angle = 35),
          axis.text.y = element_text(size = 13),
          axis.title.y = element_text(size = 13)) +
    labs(title = paste("Per 1 Million Population, COVID-19",
                  typex,
                  "Cases")) +
    theme(plot.title = element_text(size = 16))
}
  

###############################################################
###############################################################  
               
# Raw data graph
#     a = df
#     type = conf, act, death, recovered
#     region = one of the following:
#             State for US plot; or Country.Reg for worldwide plot
#     typex = conft, act, death, recovered

graph.my.data.raw <- function(a, type, region, typex) {
  ggplot(a, aes(x = date, y = type, na.rm = TRUE,
                color = region,
                group = region
  )) +
    geom_point(size = 3) + 
    geom_line(size = 2) +
    scale_colour_manual(values = cb.seven) +
    scale_x_date(date_labels="%b %d",date_breaks  ="1 week") +
    scale_y_continuous(labels = comma) +
    xlab("") +
    ylab("Total") +
    theme(panel.grid.minor = element_blank()) +
    guides(color = guide_legend(title = NULL)) +
    theme_bw() +
    theme(legend.text = element_text(size = 14)) +
    theme(axis.text.x = element_text(size = 13, angle = 35),
          axis.text.y = element_text(size = 13),
          axis.title.y = element_text(size = 13)) +
    labs(title = paste("Total Number of COVID-19",
                       typex,
                       "Cases")) +
    theme(plot.title = element_text(size = 16))
}


###############################################################
###############################################################  

# Raw data graph
#     a = df
#     type = conf, act, death, recovered
#     region = one of the following:
#             State for US plot; or Country.Reg for worldwide plot
#     typex = conft, act, death, recovered

graph.bigpic.us.raw <- function(a, type, typex) {
  a %>% 
    group_by(date) %>% 
    summarize(tot.conf = sum(us.conf),
              tot.deaths = sum(us.death),
              tot.rec = sum(us.rec),
              tot.active = sum(us.act)) %>% 
  ggplot(aes(x = date, y = type, na.rm = TRUE#,
                #color = region,
                #group = region
  )) +
    geom_point(size = 3) + 
    geom_line(size = 2) +
    #scale_colour_manual(values = cb.seven) +
    scale_x_date(date_labels="%b %d",date_breaks  ="1 week") +
    scale_y_continuous(labels = comma) +
    xlab("") +
    ylab("Total") +
    theme(panel.grid.minor = element_blank()) +
    guides(color = guide_legend(title = NULL)) +
    theme_bw() +
    theme(legend.text = element_text(size = 14)) +
    theme(axis.text.x = element_text(size = 13, angle = 35),
          axis.text.y = element_text(size = 13),
          axis.title.y = element_text(size = 13)) +
    labs(title = paste("Total Number of COVID-19",
                       typex,
                       "Cases")) +
    theme(plot.title = element_text(size = 16))
}

###############################################################
###############################################################  
###############################################################
###############################################################  

# To insert valueBox in Shiny App
  
valueBox2 <- function(value, subtitle, icon, color) {
  div(class = "col-lg-3 col-md-6",
      div(class = "panel panel-primary",
          div(class = "panel-heading", style = paste0("background-color:", color),
              div(class = "row",
                  div(class = "col-xs-3",
                      icon(icon, "fa-5x")
                  ),
                  div(class = ("col-xs-9 text-center"),
                      div(style = ("font-size: 40px; font-weight: bold;"),
                          textOutput(value)
                      ),
                      div(subtitle)
                  )
              )
          ),
          div(class = "panel-footer",
              div(class = "clearfix")
          )
      )
  )
}

###############################################################
###############################################################  

```

```{r, include=FALSE}
# Prep the Data

#  Get the global Confirmed cases information

fetchAll.conf.glob <- function(page) {
  url <- 'https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv'
  url2 <- read_html(url)
  url3 <- url2 %>%
    html_nodes("table") %>%
    .[1] %>%
    html_table(fill = TRUE)
  url4 <- data.frame(url3)
}

glob.conf <- ldply(0:0, fetchAll.conf.glob, .progress = "text")

# copy df
glob.conf2 <- glob.conf

# change column name to Confirmed
glob.conf2[,1] <- "confirmed"


###########
#  Get the global Death cases information

fetchAll.death.glob <- function(page) {
  url <- 'https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv'
  url2 <- read_html(url)
  url3 <- url2 %>%
    html_nodes("table") %>%
    .[1] %>%
    html_table(fill = TRUE)
  url4 <- data.frame(url3)
}

glob.dead <- ldply(0:0, fetchAll.death.glob, .progress = "text")

# copy df
glob.dead2 <- glob.dead

# change column name to Dead
glob.dead2[,1] <- "dead"

# Now merge df
wwdf <- bind_rows(glob.conf2, glob.dead2)

######
# change names of cells for future column names
wwdf[1, "X1"] <- "type"
wwdf[1, "X2"] <- "state"
wwdf[1, "X3"] <- "country"

# Get first row to be header row
names(wwdf) <- wwdf[1,]
wwdf <- wwdf[-1,]

# make dates their own column
wwdf <- wwdf %>% 
  pivot_longer(
    cols = "1/22/20":dim(wwdf)[2],
    names_to = "date"
  ) 

# duplicate df
wwdf3 <- wwdf

# change format of date to be Date instead of Character
wwdf3 <- wwdf3 %>% 
  mutate(date2 = date) %>% 
  separate(date, c("blah1", "blah2", "blah3"), sep = "([\\/])") %>%  # winner winner
  mutate(newmonth = blah1) %>% 
  mutate(newday = blah2) %>% 
  select(date2, newmonth, newday, blah1, blah2, blah3, everything())

# Convert blah3, newmonth and newday to numeric
wwdf3$newmonth <- as.numeric(as.character(wwdf3$newmonth))
wwdf3$newday <- as.numeric(as.character(wwdf3$newday))
wwdf3$blah3 <- as.numeric(as.character(wwdf3$blah3))

# First get month and day to be two digits each
#   Then create new date column
wwdf3 <- wwdf3 %>% 
  mutate(blah11 = sprintf("%02d", newmonth)) %>% 
  mutate(blah12 = sprintf("%02d", newday)) %>% 
  mutate(blah14 = paste("20", blah3, sep = "")) %>% 
  mutate(newdate99 = paste(blah14,
                           blah11,
                           blah12,
                           sep = "-")) %>% 
  select(newdate99, blah11, newmonth, blah12, blah14, newday, everything())

# copy the df
wwdf4 <- wwdf3

# Keep appropriate columns
wwdf4 <- wwdf4 %>% 
  mutate(date = newdate99) %>% 
  select(type, state, country, date, value, Lat, Long)

# Make value column numeric
wwdf4 <- wwdf4 %>% 
  mutate(value2 = as.numeric(as.character(value))) %>% 
  #mutate(dead2 = as.numeric(as.character(dead))) %>% 
  select(-value)

# Separate "type" column into their own columns based on type
wwdf4 <- wwdf4 %>% 
  pivot_wider(
    names_from = type,
    values_from = value2
  ) 

# change format of date to be Date instead of Character
wwdf4 <- wwdf4 %>% 
  mutate(newdate = as.Date(date, origin = "1970-01-01")) %>% 
  mutate(date = newdate) %>% 
  select(-newdate) 

maxdate <- max(wwdf4$date)

curr.ww.counts <- wwdf4 %>% 
  filter(date == maxdate) %>% 
  summarize(tot.conf = sum(confirmed, na.rm = TRUE),
            tot.dead = sum(dead, na.rm = TRUE))

curr.ww.counts
curr.ww.death.rate <- round(((curr.ww.counts$tot.dead/curr.ww.counts$tot.conf) * 100), 2)
curr.ww.death.rate

curr.us.counts <- wwdf4 %>% 
  filter(date == maxdate,
         country == "US") %>% 
  summarize(tot.conf = sum(confirmed, na.rm = TRUE),
            tot.dead = sum(dead, na.rm = TRUE))

curr.us.counts
curr.us.death.rate <- round(((curr.us.counts$tot.dead/curr.us.counts$tot.conf) * 100), 2)

#############
# worldwide data EXCLUDING USA
ww.not.us <- wwdf4 %>% 
  filter(country != "US") %>% 
  dplyr::group_by(date) %>% 
  summarize(ww.conf = sum(confirmed, na.rm = TRUE),
           ww.death = sum(dead, na.rm = TRUE)) %>% 
  mutate(region = "rest.of.world") %>% 
  gather(type, cases, ww.conf:ww.death) 

# USA only data
us.only <- wwdf4 %>% 
  filter(country == "US") %>% 
  group_by(date) %>% 
  summarize(usa.conf = sum(confirmed, na.rm = TRUE),
            usa.death = sum(dead, na.rm = TRUE)) %>% 
  mutate(region = "USA") %>% 
  gather(type, cases, usa.conf:usa.death)

# Merge worldwide NOT USA, and USA-only
mynewdf <- bind_rows(ww.not.us, us.only)

# Overall Confirmed Cases
overall.confirm.graph <- mynewdf %>% 
  filter(type == "ww.conf" | type == "usa.conf") %>% 
  ggplot(aes(x = date, y = cases, na.rm = TRUE,
             color = region,
             group = region
  )) +
  geom_point(size = 3) + 
  geom_line(size = 2) +
  scale_colour_manual(values = c(cb.blue, cb.red)) +
  scale_x_date(date_labels="%b %d",date_breaks  ="1 week") +
  scale_y_continuous(labels = comma) +
  xlab("") +
  ylab("Total") +
  theme(panel.grid.minor = element_blank()) +
  guides(color = guide_legend(title = NULL)) +
  theme_bw() +
  theme(legend.text = element_text(size = 14)) +
  theme(axis.text.x = element_text(size = 12, angle = 35),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12)) +
  labs(title = "Worldwide Total Number of COVID-19 Confirmed Cases") +
  theme(plot.title = element_text(size = 16))

overall.confirm.graph


# Death Graph
overall.death.graph <- mynewdf %>% 
  filter(type == "ww.death" | type == "usa.death") %>% 
  ggplot(aes(x = date, y = cases, na.rm = TRUE,
             color = region,
             group = region
  )) +
  geom_point(size = 3) + 
  geom_line(size = 2) +
  scale_colour_manual(values = c(cb.blue, cb.red)) +
  scale_x_date(date_labels="%b %d",date_breaks  ="1 week") +
  scale_y_continuous(labels = comma) +
  xlab("") +
  ylab("Total") +
  geom_hline(aes(yintercept = nam), color = cb.black, linetype = "dashed") +
  geom_text(aes(x=as.Date("2020-02-24"), nam, 
                label = "U.S. Deaths Vietnam", vjust = -1), size = 4.5,
            color = cb.black) +
  geom_hline(aes(yintercept = WW1), color = cb.black, linetype = "dashed") +
  geom_text(aes(x=as.Date("2020-02-24"), WW1, 
                label = "U.S. Deaths World War 1", vjust = -1), size = 4.5,
            color = cb.black) +
  #geom_hline(aes(yintercept = WW2), color = cb.black, linetype = "dashed") +
  #geom_text(aes(x=as.Date("2020-02-24"), WW2, 
  #              label = "U.S. Deaths World War 2", vjust = -1), size = 3,
  #          color = cb.black) +
  geom_hline(aes(yintercept = korean.war), color = cb.black, linetype = "dashed") +
  geom_text(aes(x=as.Date("2020-02-24"), korean.war, 
                label = "U.S. Deaths Korean War", vjust = 2), size = 4.5,
            color = cb.black) +
  geom_hline(aes(yintercept = (iraq.war + afg)), color = cb.black, linetype = "dashed") +
  geom_text(aes(x=as.Date("2020-02-24"), iraq.war + afg, 
                label = "U.S. Deaths Iraq and Afghanistan", vjust = -1), size = 4.5,
            color = cb.black) +
  theme(panel.grid.minor = element_blank()) +
  guides(color = guide_legend(title = NULL)) +
  theme_bw() +
  theme(legend.text = element_text(size = 14)) +
  theme(axis.text.x = element_text(size = 12, angle = 35),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12)) +
  labs(title = "Worldwide Total Number of COVID-19 Deaths") +
  theme(plot.title = element_text(size = 16))


overall.death.graph


################
# copy the df
wwdf5 <- wwdf4

wwdf5 <- wwdf5 %>% 
  group_by(country, date) %>% 
  summarize(tot.conf = sum(confirmed, na.rm = TRUE),
            tot.dead = sum(dead, na.rm = TRUE))
  
mycountry <- wwdf5 %>% 
  filter(country == "Italy" | country ==  "France" | country == "Germany" |
           country == "China" | country == "US" | country == "Korea, South" |
           country == "Spain") 


# Add population figures, and per capita and per 1mm info, into the data frame
mycountry <- mycountry %>% 
  mutate(pop = ifelse(country == "Italy", italypop,
                      ifelse(country == "France", frpop,
                             ifelse(country == "Germany", gerpop,
                                    ifelse(country == "China", chpop,
                                           ifelse(country == "US", uspop,
                                                  ifelse(country == "Korea, South", skpop,
                                                         spainpop))))))) %>% 
  mutate(ww.per.cap.conf = tot.conf/pop,
         ww.conf.per1mm = ww.per.cap.conf * mill,
         ww.per.cap.death = tot.dead/pop,
         ww.deaths.per1mm = ww.per.cap.death * mill
         )

#####
# Confirmed cases, selected countries
# per million
graph.conf.ww.mil <- graph.my.data.per1mm(mycountry, 
                                          mycountry$ww.conf.per1mm, 
                                          mycountry$country,
                                          "Confirmed")

graph.conf.ww.mil

# confirmed total ww pop
graph.conf.ww.raw <- graph.my.data.raw(mycountry, 
                                       mycountry$tot.conf, 
                                       mycountry$country,
                                       "Confirmed")

graph.conf.ww.raw

####
# Death cases, selected countries
# per million
graph.death.ww.mil <- graph.my.data.per1mm(mycountry, 
                                           mycountry$ww.deaths.per1mm, 
                                           mycountry$country,
                                           "Death")

graph.death.ww.mil

# total pop
graph.death.ww.raw <- graph.my.data.raw(mycountry, 
                                        mycountry$tot.dead, 
                                        mycountry$country,
                                        "Death")

graph.death.ww.raw

# ^^^^^
# |||||
# /Selected Countries


##############################################
##############################################

# Data for Individual US States
# |||||||||||||||||
# VVVVVVVVVVVVVVVVV

my.result2 <- fromJSON("https://covidtracking.com/api/v1/states/daily.json")

maxdate.us <- max(my.result2$date)

curr.us.counts.2 <- my.result2 %>% 
  filter(date == maxdate.us) %>% 
  summarize(tot.conf = sum(positive),
            tot.deaths = sum(death))

curr.us.counts.2

curr.us.death.rate <- round(((curr.us.counts.2$tot.deaths/curr.us.counts$tot.conf) * 100), 2)

# Get date column to be in date format
# copy df
usdf <- my.result2

usdf$date <- usdf$date %>% 
  lubridate::ymd()

#################
################
# US States
# |||||
# VVVVV

# Selected states
mystates <- usdf %>% 
  filter(state == "MI" | state ==  "OH" | state == "TX" |
           state == "WI" | state == "CA" | #state == "New York" |
           state == "WA" | state == "FL") 

# Add population figures, and per capita and per 1mm info, into the data frame
mystates <- mystates %>% 
  mutate(pop = ifelse(state == "MI", michpop,
                      ifelse(state == "OH", ohpop,
                             ifelse(state == "TX", txpop,
                                    ifelse(state == "WI", wipop,
                                           ifelse(state == "CA", capop,
                                                  ifelse(state == "FL", flpop,
                                                         #ifelse(state == "New York", nypop,
                                                         wapop))))))) %>% 
  mutate(per.cap.conf = positive/pop,
         conf.per1mm = per.cap.conf * mill,
         per.cap.death = death/pop,
         deaths.per1mm = per.cap.death * mill)

#####
# Confirmed cases, selected US states
# per million
graph.conf.us.mil <- graph.my.data.per1mm(mystates, 
                                          mystates$conf.per1mm, 
                                          mystates$state,
                                          "Confirmed")

graph.conf.us.mil

# total pop
graph.conf.us.raw <- graph.my.data.raw(mystates, 
                                       mystates$positive, 
                                       mystates$state,
                                       "Confirmed")

graph.conf.us.raw


#####
# Deaths cases, selected US states
graph.death.us.mil <- graph.my.data.per1mm(mystates, 
                                           mystates$deaths.per1mm, 
                                           mystates$state,
                                           "Death")

graph.death.us.mil

# total pop
graph.death.us.raw <- graph.my.data.raw(mystates, 
                                        mystates$death, 
                                        mystates$state,
                                        "Death")

graph.death.us.raw


```

Overview
==============

Row
-----------------------
### Worldwide Confirmed  

```{r , echo = FALSE}
#```{r vbox_world_confirmed, echo = FALSE}
ww_confirmed2 <- format(curr.ww.counts$tot.conf, big.mark = ",")
valueBox(value = ww_confirmed2, icon = 'fa-user-md', color = clr.ww.conf)

```


### Worldwide Deaths  
```{r vbox_world_deaths, echo = FALSE}
ww_death2 <- format(curr.ww.counts$tot.dead, big.mark = ",")
ww_pct_death = round((curr.ww.counts$tot.dead / curr.ww.counts$tot.conf) * 100, 1)
valueBox(paste(ww_death2, 
         " (", ww_pct_death, "%)"),icon = 'fa-dizzy', color = clr.ww.dead)

```


### U.S. Confirmed  
```{r , echo = FALSE}
us_confirmed2 <- format(curr.us.counts$tot.conf, big.mark = ",")
valueBox(us_confirmed2, icon = 'fa-user-md', color = clr.us.conf)

```


### U.S. Deaths  
```{r , echo = FALSE}
us_death2 <- format(curr.us.counts$tot.dead, big.mark = ",")
us_pct_death = round((curr.us.counts$tot.dead / curr.us.counts$tot.conf) * 100, 1)
valueBox(paste(us_death2,
               " (", us_pct_death, "%)"),icon = 'fa-dizzy', color = clr.us.dead)

```

Row 
-----------------------

### Worldwide Confirmed Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#```{r, fig.width=16}#, fig.height=8}
print(overall.confirm.graph)

```

Row 
-----------------------

### Worldwide Deaths Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#```{r, fig.width=16, fig.height=8}
plot(overall.death.graph)

```


Worldwide Totals
==============

Row
-----------------------
### Worldwide Confirmed  


```{r , echo = FALSE}
valueBox(ww_confirmed2, icon = 'fa-user-md', color = clr.ww.conf)

```


### Worldwide Deaths  

```{r , echo = FALSE}
#valueBox(curr.ww.counts$tot.deaths, icon = 'fa-dizzy', color = clr.ww.dead)
valueBox(paste(ww_death2, 
         " (", ww_pct_death, "%)"),icon = 'fa-dizzy', color = clr.ww.dead)

```


### U.S. Confirmed  

```{r , echo = FALSE}
valueBox(us_confirmed2, icon = 'fa-user-md', color = clr.us.conf)

```


### U.S. Deaths    
```{r , echo = FALSE}
valueBox(paste(us_death2,
               " (", us_pct_death, "%)"),icon = 'fa-dizzy', color = clr.us.dead)


```



Row  
-----------------------  

### Select Countries Confirmed Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.conf.ww.raw <- graph.my.data.raw(mycountry, 
#                                       mycountry$ww.conf, 
#                                       mycountry$Country.Reg,
#                                       "Confirmed")


plot(graph.conf.ww.raw)

```



Row  
-----------------------  

### Select Countries Deaths Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.death.ww.raw <- graph.my.data.raw(mycountry, 
#                                       mycountry$ww.death, 
#                                       mycountry$Country.Reg,
#                                       "Death")
```

```{r, echo = FALSE}
plot(graph.death.ww.raw)
```


Worldwide Per Million
==============

Row
-----------------------
### Worldwide Confirmed  


```{r , echo = FALSE}
valueBox(ww_confirmed2, icon = 'fa-user-md', color = clr.ww.conf)

```


### Worldwide Deaths  

```{r , echo = FALSE}
valueBox(paste(ww_death2, 
         " (", ww_pct_death, "%)"),icon = 'fa-dizzy', color = clr.ww.dead)

```


### U.S. Confirmed  

```{r , echo = FALSE}
valueBox(us_confirmed2, icon = 'fa-user-md', color = clr.us.conf)

```


### U.S. Deaths    
```{r , echo = FALSE}
valueBox(paste(us_death2,
               " (", us_pct_death, "%)"),icon = 'fa-dizzy', color = clr.us.dead)


```



Row  
-----------------------  

### Select Countries Confirmed Per 1 Million Population Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.conf.ww.mil <- graph.my.data.per1mm(mycountry, 
#                                          mycountry$ww.conf.per1mm, 
#                                          mycountry$Country.Reg,
#                                          "Confirmed")

graph.conf.ww.mil

```



Row  
-----------------------  

### Select Countries Deaths Per 1 Million Population Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.death.ww.mil <- graph.my.data.per1mm(mycountry, 
#                                          mycountry$ww.deaths.per1mm, 
#                                          mycountry$Country.Reg,
#                                          "Death")

graph.death.ww.mil

```


U.S. Totals
==============

Row
-----------------------
### Worldwide Confirmed  


```{r , echo = FALSE}
valueBox(ww_confirmed2, icon = 'fa-user-md', color = clr.ww.conf)

```


### Worldwide Deaths  

```{r , echo = FALSE}
#valueBox(curr.ww.counts$tot.deaths, icon = 'fa-dizzy', color = clr.ww.dead)
valueBox(paste(ww_death2, 
         " (", ww_pct_death, "%)"),icon = 'fa-dizzy', color = clr.ww.dead)

```


### U.S. Confirmed  

```{r , echo = FALSE}
valueBox(us_confirmed2, icon = 'fa-user-md', color = clr.us.conf)

```


### U.S. Deaths    
```{r , echo = FALSE}
valueBox(paste(us_death2,
               " (", us_pct_death, "%)"),icon = 'fa-dizzy', color = clr.us.dead)


```



Row  
-----------------------  

### Select U.S. States Confirmed Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.conf.us.raw <- graph.my.data.raw(mystates, 
#                                          mystates$us.conf, 
#                                          mystates$State,
#                                          "Confirmed")

plot(graph.conf.us.raw)

```



Row  
-----------------------  

### Select U.S. States Deaths Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.death.us.raw <- graph.my.data.raw(mystates, 
#                                       mystates$us.death, 
#                                       mystates$State,
#                                       "Death")

plot(graph.death.us.raw)
```

U.S. Per Million
==============

Row
-----------------------
### Worldwide Confirmed  


```{r , echo = FALSE}
valueBox(ww_confirmed2, icon = 'fa-user-md', color = clr.ww.conf)

```


### Worldwide Deaths  

```{r , echo = FALSE}
#valueBox(curr.ww.counts$tot.deaths, icon = 'fa-dizzy', color = clr.ww.dead)
valueBox(paste(ww_death2, 
         " (", ww_pct_death, "%)"),icon = 'fa-dizzy', color = clr.ww.dead)

```


### U.S. Confirmed  

```{r , echo = FALSE}
valueBox(us_confirmed2, icon = 'fa-user-md', color = clr.us.conf)

```


### U.S. Deaths    
```{r , echo = FALSE}
valueBox(paste(us_death2,
               " (", us_pct_death, "%)"),icon = 'fa-dizzy', color = clr.us.dead)


```



Row  
-----------------------  

### Select U.S. States Confirmed Per 1 Million Population Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.conf.us.mil <- graph.my.data.per1mm(mystates, 
#              mystates$conf.per1mm, 
#              mystates$State,
#              "Confirmed")

graph.conf.us.mil

```


Row  
-----------------------  

### Select U.S. States Deaths Per 1 Million Population Graph  

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#graph.death.us.mil <- graph.my.data.per1mm(mystates, 
#                                      mystates$deaths.per1mm, 
#                                      mystates$State,
#                                      "Death")

graph.death.us.mil

```


Notes
==============

Row
-----------------------
 Data come from Johns Hopkins (JH):  
 
 
   *  Updated daily at approximately 7:59pm eastern time.  
   
   *  JH pulls its data from a variety of sources, including but not limited to WHO, China CDC, US CDC, European Centre for Disease Prevention and Control, Government of Canada, etc.  
   
   *  Click here [https://github.com/CSSEGISandData/COVID-19] for direct links to data source.  
   
   *  Data are not always consistent. There are several instances of flaws in the data. JH has done an excellent job of managing the flaws, but they do continue to exist.  
   
   *  Selected U.S. states chosen based on where I have immediate family members living.  
   
   *  I can be reached via twitter @TomAlig333

